XXXXX

### 2014-09-22 paper/paper1.tex
OWL 2 QL supported and not supported constructs

>>>>

\section{Appendix}

\subsection{RDF Validation Requirements Covered by OWL 2 QL}

\begin{table}
\caption{RDF Validation Requirements Covered by OWL 2 QL}
\label{tab:RequirementsCoveredOWL2QL}
\centering
\begin{tabular}{lcccccccc}
\hr
Requirements \\
\hr
R-1-UNIQUENESS-OF-URIS \\
R-2-UNIQUE-INSTANCES \\
R-3-EQUIVALENT-CLASSES \\
R-4-EQUIVALENT-OBJECT-PROPERTIES \\
R-5-EQUIVALENT-DATA-PROPERTIES \\
\hr
\end{tabular}
\end{table}

\subsection{RDF Validation Requirements Not Covered by OWL 2 QL}

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL}
\centering
\begin{tabular}{lcccccccc}
\hr
Requirements \\
\hr
R-6-EQUIVALENT-INDIVIDUALS \\
\hr
\end{tabular}
\end{table}
